% !TeX root = main.tex

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

Many people have contributed to making this book happen.  Probably first and foremost are the many people who have done research in the area of High-Level Synthesis.  Underlying each of the applications in this book are many individual synthesis and mapping technologies which combine to result in high-quality implementations.

Many people have worked directly on the \VHLS tool over the years.  From the beginning in Jason Cong's research group at UCLA as the AutoPilot tool, to making a commercial product at AutoESL Inc., to widespread adoption at Xilinx, it's taken many hours of engineering to build an effective tool.  To Zhiru Zhang, Yiping Fan, Bin Liu, Guoling Han, Kecheng Hao, Peichen Pan, Devadas Varma, Chuck Song, and many others: your efforts are greatly appreciated.

The idea for this book originally arose out of a hallway conversation with Salil Raje shortly after Xilinx acquired the AutoESL technology.  Much thanks to Salil for his early encouragement and financial support.  Ivo Bolsens and Kees Vissers also had the trust that we could make something worth the effort.  Thanks to you all for having the patience to wait for good things to emerge.

This book would not have been possible without substantial support from the UCSD Wireless Embedded Systems Program. This book grew out of the need to make a hardware design class that could be broadly applicable to students coming from a mix of software and hardware backgrounds.  The program provided substantial resources in terms of lab instructors, teaching assistants, and supplies that were invaluable as we developed (and re-developed) the curriculum that eventually morphed into this book. Thanks to all the UCSD 237C students over the years for providing feedback on what made sense, what didn't, and generally acting as guinea pigs over many revisions of the class and this book. Your suggestions and feedback were extremely helpful. A special thanks to the TAs for these classes, notable Alireza Khodamoradi, Pingfan Meng, Dajung Lee, Quentin Gautier, and Armaiti Ardeshiricham; they certainly felt the growing pains a lot more than the instructor.

Various colleagues have been subjected to early drafts of the book, including Zhiru Zhang, Mike Wirthlin, Jonathan Corbett. We appreciate your feedback.  